### 2020-04-19 tables/01_predictors.Rmd
add latex table placeholders

options(knitr.kable.NA = " - ")
knitr::kable(dt, digits = 0, format = "markdown") 
#%>%
 # add_header_above(c(" ", " ", Ranges = 3, " ", " "))
```

>>>>

options(knitr.kable.NA = " - ")
knitr::kable(dt, digits = 0, format = "markdown") 
# knitr::kable(dt, format = 'latex', align = c("lllll"))
#%>%
 # add_header_above(c(" ", " ", Ranges = 3, " ", " "))
```

### 2020-04-19 tables/03_model_summary.Rmd
add latex table placeholders

options(knitr.kable.NA = "-")  
dt %>%
  # dplyr::filter(str_detect(response, "tp")) %>%
  # dplyr::select(-response) %>%
  dplyr::rename("$R^2$" = r2, 
                "LOO-ELPD" = elpd_diff) %>%
  knitr::kable(digits = 2, format = "markdown", caption = "TP Model R2", 
               row.names = FALSE)
```

>>>>

options(knitr.kable.NA = "-")  
dt %>%
  # dplyr::filter(str_detect(response, "tp")) %>%
  # dplyr::select(-response) %>%
  dplyr::rename("$R^2$" = r2, 
                "LOO-ELPD" = elpd_diff) %>%
  knitr::kable(digits = 2, format = "markdown", caption = "TP Model R2",
               row.names = FALSE)
# knitr::kable(digits = 2, format = 'latex', align = c("lllll"), row.names = FALSE)
```
